---
title: "homework"
author: "LZH-XX"
date: "12/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##1. The optimization target and their dual gap and dual residual

### Lasso

$\bar{g}_{i}^{*}\left(u_{i}\right)=\max _{\alpha_{i}:\left|\alpha_{i}\right| \leq B} u_{i} \alpha_{i}-\lambda\left|\alpha_{i}\right|=B\left[\left|u_{i}\right|-\lambda\right]_{+}$

```{r positive}
positive <- function(x){
  if(x >= 0){
    return(x)
  }
  return(0)
}
```

```{r lasso.loss}
lasso.loss <- function(A,alpha,y) {
  # 返回loss函数的值
  return ((norm(as.matrix(A%*%alpha - y),type = "2"))^2)
          #+norm("alpha",type = "O"))
}
```

```{r lasso.w_func}
lasso.w_func <- function(alpha,A,y){
  #返回w的函数值
  return(2*(A %*% alpha - y))
}
```

```{r lasso.subgrad}
lasso.subgrad <- function(alpha,lambda,A,dimension,y,...){
  #返回次梯度
  i <- dimension
  n <- length(alpha)
  #alpha0 <- as.matrix(alpha)
  # First calculate the subgrad of |alpha|, sub1
  if (alpha[i] > 0 ){
    sub1 <- lambda#alpha[i]/norm(alpha0,type = "O")
  }
  else if(alpha[i] < 0){
    sub1 <- -lambda#alpha[i]/norm(alpha0,type = "O")
  }
  else {
    seed <- 0#runif(1,-1,1)
    sub1 <- lambda*seed #* alpha[i]/norm(alpha0,type = "O")
  }
  # Then calculate the grad of ||A\alpha -y||^2
  #term <- vector(length =length(A[,1]))
  #for (s in 1:n){
  #  term <- term + as.vector(alpha[s]*A[,s])
  #}
  #sub2 <- t(A[,i]) %*% term + t(term) %*% A[,i] - t(y) %*% A[,i] - t(A[,i])%*% y
  term <- 2*(A%*%alpha-y)
  term <- as.vector(term)
  sub2 <- sum(A[,i]*term)
  subgrad = sub1 + sub2 #rowSums(sub2)
  #browser()
  return(subgrad)
}
```

```{r lasso.gap}
lasso.gap <- function(alpha,lambda,B,A,dimension,y){
  # 计算对偶gap
  # A is a matrix
  i <- dimension
  #browser()
  w <- lasso.w_func(alpha,A,y)
  gap <- B*positive(abs(sum(A[,i]* w))- lambda)+lambda*abs(alpha[i])+alpha[i]*(sum(A[,i]* w))
  #browser()
  return(gap)
}
#CD_each_iter(sample_p = p.uniform,A =diag(1,3,3) ,y = diag(1,3,3)%*%c(1,0,1),lambda = 0.05)
```

```{r lasso.dualres}
lasso.dualres <- function(alpha,lambda,A,dimension,y, B){
  #计算对偶残差
  # first calculate the subgrad of g_i^*
  i <- dimension
  flag <-  0
  eps <- 1e-5
  w <- lasso.w_func(alpha, A, y)
  input <- -t(A[,i])%*%w
  #browser()
  # 这里的g用的是文中修改后的g拔，下面计算次梯度
  if (input <= -lambda - eps){
    g_sub <- -B
  }
  else if(input >= lambda + eps){
    g_sub <- B
  }
  else if(input > -lambda + eps & input < lambda + eps){
    g_sub <- 0
  }
  else if(input < 0){
    g_sub_right <- 0
    g_sub_left  <- -B
    flag <- 1 
    #g_sub is an interval
  }
  else{
    g_sub_right <- B
    g_sub_left  <- 0
    flag <- 1 
    #g_sub is an interval
  }
  # When flag ==0 ,subgrad is grad, otherwise is a interval
  if (flag == 0){
      return (abs(alpha[i]-g_sub))
  }
  #  subgrad is a interval
  if (alpha[i] >= g_sub_left & alpha[i] <= g_sub_right){
    return (0)
  }
  else {
    return (min(abs(alpha[i]-g_sub_right),abs(alpha[i]-g_sub_left) ))
    # Return the closet distance from the interval
  }
}
#CD_each_iter(sample_p = p.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05)
```

```{r svm.loss}
svm.loss <- function(A,alpha,lambda = 0.1,y) {
  # 返回loss函数的值
  n <- dim(A)[2]
  #browser()
  loss <- (norm(as.matrix(A%*%alpha ),type = "2"))^2/(n^2 * lambda * 2)-sum(alpha*y)/n
  #browser()
  return (loss)
}
```

```{r svm.gap}
svm.gap <- function(alpha,lambda = 0.1,A,dimension,y,w){
  # 计算对偶gap
  # A is a matrix
  i <- dimension
  n <- dim(A)[2]
  #browser()
  #w <- lasso.w_func(alpha,A,y)
  gap <- positive(1-y[i]*sum(A[,i]*w))/n - alpha[i]*y[i]/n + alpha[i]*sum(A[,i]*w)
  #browser()
  if(gap < 0){
    return(0)
  }
  return(gap)
}

```

```{r svm.dualres}
svm.dualres <- function(A,dimension,y,w,alpha){
  #计算对偶残差

  i <- dimension
  n <- dim(A)[2]
  flag <-  0
  eps <- 1e-5
  input <- -t(A[,i])%*%w
  #browser()
  if (y[i]==1){
    if (input <= -1 - eps){
    g_sub <- 0
   }else if(input >= -1 + eps){
     g_sub <- 1/n
   }else{
    g_sub_right <- 1/n
    g_sub_left  <- 0
    flag <- 1 
    #g_sub is an interval
  }
  }else{
    if (input <= 1 - eps){
    g_sub <- -1/n
   }else if(input >= 1 + eps){
     g_sub <- 0
   }else{
    g_sub_right <- 0
    g_sub_left  <- -1/n
    flag <- 1 
    #g_sub is an interval
  }
  }
  #browser()
  # When flag ==0 ,subgrad is grad, otherwise is a interval
  if (flag == 0){
      return (abs(alpha[i]-g_sub))
  }
  #  subgrad is a interval
  if (alpha[i] >= g_sub_left & alpha[i] <= g_sub_right){
    return (0)
  }
  else {
    return (min(abs(alpha[i]-g_sub_right),abs(alpha[i]-g_sub_left) ))
    # Return the closet distance from the interval
  }
}

```

##2.Adaptive Sampling -based CD 

###2.1 Gap-wise
```{r p.ada.gap}
p.ada.gap <- function(alpha,lambda,B,A,y){
  n <- length(alpha)
  p <- numeric(length = n)
  for (i in 1:n){
    p[i] <- lasso.gap(alpha, lambda, B, A, i, y)
    #browser()
  }
  #browser()
  psum <- sum(p) 
  for (i in 1:n){
    p[i] <- p[i]/psum
  }
  return(p)
}
```

```{r svm.p.ada.gap}
svm.p.ada.gap <- function(alpha,lambda = 0.1,A,y,w){
  n <- length(alpha)
  p <- numeric(length = n)
  for (i in 1:n){
    p[i] <- svm.gap(alpha = alpha, A = A, y = y, dimension = i, w = w)
    #browser()
  }
  #browser()
  psum <- sum(p) 
  for (i in 1:n){
    p[i] <- p[i]/psum
  }
  return(p)
}
```

###2.2 Adaptive

```{r p.ada.uniform}
p.ada.uniform <- function(alpha, lambda, A, y, sigma,B){
  n <- length(alpha)
  p <- rep(1,n)
  second_term <- numeric(length = n)
  eps <- 1e-5
  m <- n
  for (i in 1:n){
    k <- abs(lasso.dualres(alpha, lambda, A, i,y, B))
    if( k < eps){
      p[i] <- 0
      m <- m-1
    }else{
      second_term[i] <- k*norm(as.matrix(A[,i]),type ="F")
    }
    
    #browser()
  }
  second_term <- second_term/sum(second_term)
  for(i in 1:n){
    if(p[i]==1){
      p[i] = sigma/m
    }
  }
 
  p <- p + second_term*(1-sigma)
  #browser()
  return(p)
}
```

```{r svm.p.ada.uniform}
svm.p.ada.uniform <- function(alpha,lambda = 0.1,A,y,w, sigma){
  n <- length(alpha)
  p <- rep(1,n)
  second_term <- numeric(length = n)
  eps <- 1e-5
  m <- n
  for (i in 1:n){
    k <- abs(svm.dualres(A = A, y = y, w = w, dimension = i, alpha = alpha))
    #browser()
    if( k < eps){
      p[i] <- 0
      m <- m-1
    }else{
      second_term[i] <- k*norm(as.matrix(A[,i]),type ="F")
    }
    
    #browser()
  }
  second_term <- second_term/sum(second_term)
  for(i in 1:n){
    if(p[i]==1){
      p[i] = sigma/m
    }
  }
 
  p <- p + second_term*(1-sigma)
  
  #browser()
  return(p)
}
```
###2.3 Uniform

```{r p.uniform}
p.uniform <- function(alpha,A,y,lambda,B){
  n <- length(alpha)
  p <- numeric(length = n)
  for (i in 1:n){
    p[i] <- 1/n
  }
  return(p)
}
```

```{r svm.p.uniform}
svm.p.uniform <- function(alpha,lambda = 0.1,A,y,w){
  n <- length(alpha)
  p <- numeric(length = n)
  for (i in 1:n){
    p[i] <- 1/n
  }
  return(p)
}
```
###2.4 Importance Sampling

```{r p.imp}
p.imp <- function(alpha,A,y,lambda,B){
  n <- length(alpha)
  p <- numeric(length = n)
  for (i in 1:n){
    p[i] <- norm(as.matrix(A[,i]),type = "F")
  }
  p = p/sum(p)
  return(p)
}
```

```{r svm.p.imp}
svm.p.imp <- function(alpha,lambda = 0.1,A,y,w){
  n <- length(alpha)
  p <- numeric(length = n)
  for (i in 1:n){
    p[i] <- norm(as.matrix(A[,i]),type = "F")
  }
  p = p/sum(p)
  return(p)
}
```
##3.Coordinate descdent

```{r CD_each_iter}
CD_each_iter <- function(sample_p,A,y,lambda,step0 = 0.1,...)
  {
  record_length <- 25
  epoch <- dim(A)[2]
  n <- dim(A)[2]
  alpha <- numeric(n)
  max_iter <- epoch*record_length
  record.gap <- numeric(length=record_length)
  record.loss <- numeric(length=record_length)
  gap <- numeric(n)
  # A,y are given data
  #browser()
  B <- (norm(A%*%alpha - y,type = "2"))^2/lambda + sum(abs(alpha))
  w <- lasso.w_func(alpha,A,y)
  iter <- 0
  while(iter < max_iter){
  iter <- iter+1
  i <- sample(1:n,size = 1,prob = sample_p(alpha = alpha,A=A,y=y,lambda=lambda,B=B,...))
  
  update <- lasso.subgrad(alpha = alpha,dimension =i ,A =A,y=y,lambda = lambda)
  inverses <- max(2*sum(A[,i]**2),1)
  #inverses <- 2*sum(A[,i]**2)
  alpha[i] <- alpha[i] - step0*update/inverses
  #alpha_ <- alpha - step0*update/inverses
  #if (lasso.loss(A,alpha_,y) < lasso.loss(A,alpha,y) ){
  #   alpha <- alpha_ 
  #   iter <- iter+1
  #}
  #if (iter %%10 == 0){
  #  print("w")
  #  w <- lasso.w_func(alpha,A,y)
  #  print(sum(w**2))}
  #browser()
  # Record the result
  if(iter%%epoch==0){
    k <- iter/epoch
    for(j in 1:n){
      gap[j] <- lasso.gap(alpha, lambda, B, A, j,y=y)
    }
    record.gap[k] <- sum(gap)
    #print(lasso.loss(A = A,alpha = alpha,y = y))
    record.loss[k] <- lasso.loss(A, alpha, y)
    #browser()
  }
  }
  result <- list(dual.gap = log(record.gap), suboptimality = log(record.loss))
  #browser()
  return (result)
}
#CD_each_iter(sample_p = p.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05)
```

```{r CD_per_epoch}
CD_per_epoch <- function(sample_p,A,y,lambda,step0 = 0.1,...)
  {
  record_length <- 25
  epoch <- dim(A)[2]
  n <- dim(A)[2]
  alpha <- numeric(n)
  max_iter <- epoch*record_length
  record.gap <- numeric(length=record_length)
  record.loss <- numeric(length=record_length)
  gap <- numeric(n)
  # A,y are given data
  #browser()
  B <- (norm(A%*%alpha - y,type = "2"))^2/lambda + sum(abs(alpha))
  w <- lasso.w_func(alpha,A,y)
  iter <- 0
  p <- sample_p(alpha = alpha, A = A, y = y, lambda = lambda, B = B, ...)
  while(iter < max_iter){
  iter <- iter+1
  i <- sample(1:n,size = 1,prob = p)
  update <- lasso.subgrad(alpha = alpha,dimension =i ,A =A,y=y,lambda = lambda)
  inverses <- max(2*sum(A[,i]**2),1)
  #inverses <- 2*sum(A[,i]**2)
  alpha[i] <- alpha[i] - step0*update/inverses
  #browser()
  # Record the result
  if(iter%%epoch==0){
    k <- iter/epoch
    for(j in 1:n){
      gap[j] <- lasso.gap(alpha, lambda, B, A, j,y=y)
    }
    record.gap[k] <- sum(gap)
    #print(lasso.loss(A = A,alpha = alpha,y = y))
    record.loss[k] <- lasso.loss(A, alpha, y)
    p <- sample_p(alpha = alpha, A = A, y = y, lambda = lambda, B = B, ...)
    #browser()
  }
  }
  result <- list(dual.gap = log(record.gap), suboptimality = log(record.loss))
  #browser()
  return (result)
}
#CD_each_iter(sample_p = p.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05)
```

```{r svm_CD_each_iter}
svm_CD_each_iter <- function(sample_p,A,y,lambda = 0.1,step0 = 0.1,...)
  {
  record_length <- 10
  epoch <- dim(A)[2]
  n <- dim(A)[2]
  #alpha <- numeric(n)
  #w <- numeric(length = dim(A)[1])
  alpha <- rep(1,n)
  w <- A%*%alpha/lambda/n^2
  max_iter <- epoch*record_length
  record.gap <- numeric(length=record_length)
  record.loss <- numeric(length=record_length)
  gap <- numeric(n)
  # A,y are given data
  
  
  iter <- 0
  while(iter < max_iter){
  
  iter <- iter+1
  #browser()
  
  p = sample_p(alpha = alpha,A=A,y=y,lambda=lambda,w = w,...)
  
  #browser()
  i <- sample(1:n,size = 1,prob = p)
  #update <- y[i]*max(0,min(1,y[i]*alpha[i]+(1-y[i]*sum(A[,i]*w))/(sum(A[,i]**2)/(lambda*n)))) - alpha[i]
  #alpha[i] <- update +alpha[i]
  #w <- w + A[,i]*update/(lambda*n)
  grad <- -y[i]/n + sum(as.vector(A%*%alpha)*A[,i])/lambda/(n^2)
  alpha[i] <- alpha[i]- step0*grad
  w <- A%*%alpha/lambda/n^2
  
  #browser()
  if(iter%%epoch==0){
    k <- iter/epoch
    for(j in 1:n){
      gap[j] <- svm.gap(alpha = alpha, A = A, y = y, dimension = j, w = w, lambda = lambda)
    }
    record.gap[k] <- sum(gap)

    record.loss[k] <- svm.loss(A, alpha, lambda,y)
    #browser()
  }
  
  }
  result <- list(dual.gap = log(record.gap), svm = record.loss)
  #browser()
  return (result)
}

```

```{r svm_CD_per_epoch}
svm_CD_per_epoch <- function(sample_p,A,y,lambda = 0.1,step0 = 0.1,...)
  {
  record_length <- 10
  epoch <- dim(A)[2]
  n <- dim(A)[2]
  #alpha <- numeric(n)
  #w <- numeric(length = dim(A)[1])
  alpha <- rep(1,n)
  w <- A%*%alpha/lambda/n^2
  max_iter <- epoch*record_length
  record.gap <- numeric(length=record_length)
  record.loss <- numeric(length=record_length)
  gap <- numeric(n)
  # A,y are given data
  
  p = sample_p(alpha = alpha,A=A,y=y,lambda=lambda,w = w,...)
  iter <- 0
  while(iter < max_iter){
  iter <- iter+1
  i <- sample(1:n,size = 1,prob = p)
  #update <- y[i]*max(0,min(1,y[i]*alpha[i]+(1-y[i]*sum(A[,i]*w))/(sum(A[,i]**2)/(lambda*n)))) - alpha[i]
  #alpha[i] <- update +alpha[i]
  #w <- w + A[,i]*update/(lambda*n)
  grad <- -y[i]/n + sum(as.vector(A%*%alpha)*A[,i])/lambda/(n^2)
  alpha[i] <- alpha[i]- step0*grad
  w <- A%*%alpha/lambda/n^2
  #browser()
  if(iter%%epoch==0){
    k <- iter/epoch
    for(j in 1:n){
      gap[j] <- svm.gap(alpha = alpha, A = A, y = y, dimension = j, w = w, lambda = lambda)
    }
    record.gap[k] <- sum(gap)

    record.loss[k] <- svm.loss(A, alpha, lambda,y)
    #browser()
    p = sample_p(alpha = alpha,A=A,y=y,lambda=lambda,w = w,...)
  }
  
  }
  result <- list(dual.gap = log(record.gap), svm = record.loss)
  #browser()
  return (result)
}

```
##4.Exmperiment

Collect data
```{r get_dataset}
mushrooms <- readLines("https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/mushrooms")
rcv1 <- readLines("rcv1_train.binary")
ionosphere <- readLines("https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/ionosphere_scale")
```
Get corresponding A and y
```{r mushrooms_A&y}
A.mushrooms <- matrix(0,nrow = 8124, ncol = 112)
y.mushrooms <- numeric(length = 112)
a <- strsplit(mushrooms, split = " ")
for(i in 1:8124){
  b <- a[[i]]
  y.mushrooms[i] <- as.numeric(b[1])
  b <- b[-1]
  len <- length(b)
  c <- strsplit(b,split = ":")
  for(j in 1:len){
    colind <- c[[j]][1]
    val <- c[[j]][2]
    colind <- as.numeric(colind)
    val <- as.numeric(val)
    A.mushrooms[i,colind] <- val
  }
}
```

```{r rcv1_A&y}
set.seed(100)
ind <- sample(1:20242, 8000)
feature <- sample(1:50000, 300)
feature <- as.character(sort(feature))
rcv1 <- rcv1[ind]
A.rcv1 <- matrix(0,nrow = 8000, ncol = 300)
colnames(A.rcv1) <- feature
y.rcv1 <- numeric(length = 8000)
a <- strsplit(rcv1, split = " ")
for(i in 1:8000){
  b <- a[[i]]
  y.rcv1[i] <- as.numeric(b[1])
  b <- b[-1]
  len <- length(b)
  c <- strsplit(b,split = ":")
  #browser()
  for(j in 1:len){
    colind <- c[[j]][1]
    if(sum(colind==feature)==1){
      val <- c[[j]][2]
      val <- as.numeric(val)
      A.rcv1[i,colind] <- val
    }
  }
}
```
remove rows and columns that are full of 0 in A.rcv1
```{r pre_process_rcv1}
rs<-apply(A.rcv1,1,sum)
A.rcv1 <- A.rcv1[which(rs!=0),]
y.rcv1 <- y.rcv1[which(rs!=0)]
cs <- apply(A.rcv1,2,sum)
A.rcv1 <- A.rcv1[,which(cs!=0)]
```


```{r ionosphere_A&y}
A.ionosphere <- matrix(0,nrow = 351, ncol = 34)
y.ionosphere <- numeric(length = 351)
a <- strsplit(ionosphere, split = " ")
for(i in 1:351){
  b <- a[[i]]
  y.ionosphere[i] <- as.numeric(b[1])
  b <- b[-1]
  len <- length(b)
  c <- strsplit(b,split = ":")
  for(j in 1:len){
    colind <- c[[j]][1]
    val <- c[[j]][2]
    colind <- as.numeric(colind)
    val <- as.numeric(val)
    A.ionosphere[i,colind] <- val
  }
}

```

```{r}
A.ionosphere <- A.ionosphere[,-2]
A.ionosphere <- t(A.ionosphere)
```
example


```{r glm_try, eval=FALSE}
glmnet.fit<- cv.glmnet( A.mushrooms,y.mushrooms ,family = "multinomial")
g.coef <- coef(glmnet.fit)
n=112
alpha1 = numeric(n)
for (mmm in 1:n){
  alpha1[mmm] = runif(1,-1,-0.5)#g.coef[[1]][mmm]
}
sum((A.mushrooms%*%alpha1-y.mushrooms)^2)
n=112
alpha1 = numeric(n)
for (mmm in 1:n){
  alpha1[mmm] = g.coef[[1]][mmm]
}
```


```{r small_data_for_debug, eval=FALSE}
d = length(alpha1)
A = A.mushrooms[1:200,]
y = A%*%alpha1
alpha = numeric(d)
#CD_each_iter(sample_p = p.imp,A = A,y = y,lambda = 0.05,step0 = 0.5)
```

```{r full_data_for_degug, eval=FALSE}
CD_each_iter(sample_p = p.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
```

## 5.Plot

```{r save_result}
save_result <- function(CD, name, ...){
  result.gap <- matrix(0,nrow = 5, ncol = 25)
  result.loss <- matrix(0, nrow = 5, ncol = 25)
  for (i in 1:5){
    result <- CD(...)
   result.gap[i,] <- result$dual.gap
   result.loss[i,] <- result$suboptimality
  }
  name1 <- paste0("result/", name, "_gap.csv")
  name2 <- paste0("result/", name, "_loss.csv")
  write.csv(as.data.frame(result.gap),file = name1)
  write.csv(as.data.frame(result.loss),file = name2)
}
```

```{r svm_save_result}
svm_save_result <- function(CD, name, ...){
  result.gap <- matrix(0,nrow = 5, ncol = 10)
  result.loss <- matrix(0, nrow = 5, ncol = 10)
  for (i in 1:5){
    result <- CD(...)
   result.gap[i,] <- result$dual.gap
   result.loss[i,] <- result$svm
  }
  name1 <- paste0("svm/", name, "_gap.csv")
  name2 <- paste0("svm/", name, "_loss.csv")
  write.csv(as.data.frame(result.gap),file = name1)
  write.csv(as.data.frame(result.loss),file = name2)
}
```

```{r collect_data_each_iter_mushrooms, eval=FALSE}
save_result(CD_each_iter, "uni", sample_p = p.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
save_result(CD_each_iter, "ssuni", sample_p = p.ada.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1,sigma=1)
save_result(CD_each_iter, "adative", sample_p = p.ada.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1,sigma=0)
save_result(CD_each_iter, "adauni", sample_p = p.ada.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1,sigma=0.5)
save_result(CD_each_iter, "imp", sample_p = p.imp,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
save_result(CD_each_iter, "adagap", sample_p = p.ada.gap,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
```


```{r collect_data_per_epoch_mushrooms, eval = FALSE}
save_result(CD_per_epoch, "epoch_adagap", sample_p = p.ada.gap,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
save_result(CD_per_epoch, "epoch_imp", sample_p = p.imp,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
save_result(CD_each_iter, "epoch_uni", sample_p = p.uniform,A = A.mushrooms,y = y.mushrooms,lambda = 0.05,step0 = 1)
```

```{r result_cv1, eval=FALSE}
#save_result(CD_each_iter, "uni_rcv", sample_p = p.uniform,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1)
save_result(CD_each_iter, "ssuni_rcv", sample_p = p.ada.uniform,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1, sigma = 1)
save_result(CD_each_iter, "adative_rcv", sample_p = p.ada.uniform,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1, sigma = 0)
save_result(CD_each_iter, "adauni_rcv", sample_p = p.ada.uniform,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1, sigma = 0.5)
save_result(CD_each_iter, "imp_rcv", sample_p = p.imp,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1)
save_result(CD_each_iter, "adagap_rcv", sample_p = p.ada.gap,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1)


save_result(CD_per_epoch, "epoch_uni_rcv", sample_p = p.uniform,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1)
save_result(CD_per_epoch, "epoch_imp_rcv", sample_p = p.imp,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1)
save_result(CD_per_epoch, "epoch_adagap_rcv", sample_p = p.ada.gap,A = A.rcv1,y = y.rcv1,lambda = 7e-4,step0 = 1)
```

```{r ionosphere result eval=FALSE}
svm_save_result(svm_CD_each_iter, "uni", sample_p = svm.p.uniform,A = A.ionosphere,y = y.ionosphere,step0 = 30)

svm_save_result(svm_CD_each_iter, "ssuni", sample_p = svm.p.ada.uniform,A = A.ionosphere,y = y.ionosphere,step0 = 30, sigma = 1)

svm_save_result(svm_CD_each_iter, "adative", sample_p = svm.p.ada.uniform,A = A.ionosphere,y = y.ionosphere,step0 = 30, sigma = 0)

svm_save_result(svm_CD_each_iter, "adauni", sample_p = svm.p.ada.uniform,A = A.ionosphere,y = y.ionosphere,step0 = 30, sigma = 0.5)

svm_save_result(svm_CD_each_iter, "imp", sample_p = svm.p.imp,A = A.ionosphere,y = y.ionosphere,step0 = 30)

svm_save_result(svm_CD_each_iter, "adagap", sample_p = svm.p.ada.gap,A = A.ionosphere,y = y.ionosphere,step0 = 30)

svm_save_result(svm_CD_per_epoch, "epoch_uni", sample_p = svm.p.uniform,A = A.ionosphere,y = y.ionosphere,step0 = 30)

svm_save_result(svm_CD_per_epoch, "epoch_imp", sample_p = svm.p.imp,A = A.ionosphere,y = y.ionosphere,step0 = 30)

svm_save_result(svm_CD_per_epoch, "epoch_adagap", sample_p = svm.p.ada.gap,A = A.ionosphere,y = y.ionosphere,step0 = 30)
```

```{r process_result}
process_result <- function(df){
  return(apply(df, 2, mean))
}
```


```{r intial gap and loss of mushrooms}
B <- (norm(y.mushrooms,type = "2"))^2/0.05
gap0 <- 0
for (i in 1:112){
  gap0 <- gap0 + lasso.gap(numeric(112),0.05,B,A.mushrooms,i,y.mushrooms)
}
gap0 <- log(gap0)
loss0 <- lasso.loss(A.mushrooms,numeric(112),y.mushrooms)
loss0 <- log(loss0)
cat("B is",B, "\nlog of dual gap is",gap0)
```


```{r plot mushroom per epoch}
gap.adagap.e <- process_result(read.csv("result/epoch_adagap_gap.csv"))[-1]
gap.uni.e <- process_result(read.csv("result/epoch_uni_gap.csv"))[-1]
gap.imp.e <- process_result(read.csv("result/epoch_imp_gap.csv"))[-1]
loss.adagap.e <- process_result(read.csv("result/epoch_adagap_loss.csv"))[-1]
loss.uni.e <- process_result(read.csv("result/epoch_uni_loss.csv"))[-1]
loss.imp.e <- process_result(read.csv("result/epoch_imp_loss.csv"))[-1]
gap.adagap.e <- c(gap0,gap.adagap.e[1:20])
gap.uni.e <- c(gap0,gap.uni.e[1:20])
gap.imp.e <- c(gap0,gap.imp.e[1:20])
loss.adagap.e <- c(loss0,2*loss.adagap.e[1:20])
loss.uni.e <- c(loss0,2*loss.uni.e[1:20])
loss.imp.e <- c(loss0,2*loss.imp.e[1:20])
jpeg("figure/mushrooms1.jpeg",width = 1200)
par(mfrow = c(1,2))
plot(1:21, gap.adagap.e, col = "gold", xlab = "Epochs", ylab = "log of dual gap", type = "l",main = "dual gap of mushrooms", lwd = 2)
lines(1:21, gap.imp.e, col = "orangered", xlab = "Epochs", ylab = "log of dual gap", lwd =2 )
lines(1:21, gap.uni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of dual gap", type = "l", lwd =2)
legend("topright", col = c("dodgerblue","orangered","gold"),lwd=2,lty = 1, legend = c("uniform","importance", "gap-per-epoch"))
plot(1:21, loss.adagap.e, col = "gold", xlab = "Epochs", ylab = "log of suboptimality", type = "l", main = "suboptimality of mushrooms",lwd = 2)
lines(1:21, loss.imp.e, col = "orangered", lwd = 2)
lines(1:21, loss.uni.e, col = "dodgerblue", lwd =2)
legend("topright", col = c("dodgerblue","orangered","gold"),lwd=2,lty = 1, legend = c("uniform","importance", "gap-per-epoch"))
dev.off()
```

```{r plot mushroom each iter}
gap.adagap.e <- process_result(read.csv("result/adagap_gap.csv"))[-1]
gap.imp.e <- process_result(read.csv("result/imp_gap.csv"))[-1]
gap.ssuni.e <- process_result(read.csv("result/ssuni_gap.csv"))[-1]
gap.adative.e <- process_result(read.csv("result/adative_gap.csv"))[-1]
gap.adauni.e <- process_result(read.csv("result/adauni_gap.csv"))[-1]

loss.adagap.e <- process_result(read.csv("result/adagap_loss.csv"))[-1]
loss.imp.e <- process_result(read.csv("result/imp_loss.csv"))[-1]
loss.ssuni.e <- process_result(read.csv("result/ssuni_loss.csv"))[-1]
loss.adative.e <- process_result(read.csv("result/adative_loss.csv"))[-1]
loss.adauni.e <- process_result(read.csv("result/adauni_loss.csv"))[-1]

gap.adagap.e <- c(gap0,gap.adagap.e[1:20])
gap.imp.e <- c(gap0,gap.imp.e[1:20])
gap.ssuni.e <- c(gap0,gap.ssuni.e[1:20])
gap.adative.e <- c(gap0,gap.adative.e[1:20])
gap.adauni.e <- c(gap0,gap.adauni.e[1:20])

loss.adagap.e <- c(loss0,2*loss.adagap.e[1:20])
loss.imp.e <- c(loss0,2*loss.imp.e[1:20])
loss.ssuni.e <- c(loss0,2*loss.ssuni.e[1:20])
loss.adative.e <- c(loss0,2*loss.adative.e[1:20])
loss.adauni.e <- c(loss0,2*loss.adauni.e[1:20])

jpeg("figure/mushrooms2.jpeg",width = 1200)
par(mfrow = c(1,2))
plot(1:21, gap.ssuni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of dual gap", type = "l",main = "dual gap of mushrooms",lwd = 2, ylim = c(17, 26))
lines(1:21, gap.adative.e, col = "orangered", lwd = 2)
lines(1:21, gap.adauni.e, col = "gold", lwd = 2)
lines(1:21, gap.adagap.e, col = "purple", lwd = 2)
lines(1:21, gap.imp.e, col = "lightcyan3", lty = 2, lwd = 2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","importance"))
plot(1:21, loss.ssuni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of suboptimality", type = "l",lwd=2, main = "suboptimality of mushrooms",ylim = c(2, 10))
lines(1:21, loss.adative.e, col = "orangered",lwd=2)
lines(1:21, loss.adauni.e, col = "gold",lwd=2)
lines(1:21, loss.adagap.e, col = "purple",lwd=2)
lines(1:21, loss.imp.e, col = "lightcyan3", lty = 2,lwd=2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","importance"))
dev.off()
```



```{r intial gap and loss of rcv1}
B <- (norm(y.rcv1,type = "2"))^2/7e-4
gap0 <- 0
for (i in 1:dim(A.rcv1)[2]){
  gap0 <- gap0 + lasso.gap(numeric(dim(A.rcv1)[2]),7e-4,B,A.rcv1,i,y.rcv1)
}
gap0 <- log(gap0)
loss0 <- lasso.loss(A.rcv1,numeric(dim(A.rcv1)[2]),y.rcv1)
loss0 <- log(loss0)
cat("B is",B, "\nlog of dual gap is",gap0)
```

```{r plot rcv1 per epoch}
gap.adagap.e <- process_result(read.csv("result/epoch_adagap_rcv_gap.csv"))[-1]
gap.uni.e <- process_result(read.csv("result/epoch_uni_rcv_gap.csv"))[-1]
gap.imp.e <- process_result(read.csv("result/epoch_imp_rcv_gap.csv"))[-1]
loss.adagap.e <- process_result(read.csv("result/epoch_adagap_rcv_loss.csv"))[-1]
loss.uni.e <- process_result(read.csv("result/epoch_uni_rcv_loss.csv"))[-1]
loss.imp.e <- process_result(read.csv("result/epoch_imp_rcv_loss.csv"))[-1]
gap.adagap.e <- c(gap0,gap.adagap.e[1:20])
gap.uni.e <- c(gap0,gap.uni.e[1:20])
gap.imp.e <- c(gap0,gap.imp.e[1:20])
loss.adagap.e <- c(loss0,2*loss.adagap.e[1:20])
loss.uni.e <- c(loss0,2*loss.uni.e[1:20])
loss.imp.e <- c(loss0,2*loss.imp.e[1:20])
jpeg("figure/rcv1_1.jpeg",width = 1200)
par(mfrow = c(1,2))
plot(1:21, gap.adagap.e, col = "gold", xlab = "Epochs", ylab = "log of dual gap", type = "l",main = "dual gap of rcv1", lwd =2)
lines(1:21, gap.imp.e, col = "orangered", lwd =2)
lines(1:21, gap.uni.e, col = "dodgerblue", lwd =2)
legend("topright", col = c("dodgerblue","orangered","gold"),lty = 1, legend = c("uniform","importance", "gap-per-epoch"),lwd = 2)
plot(1:21, loss.adagap.e, col = "gold", xlab = "Epochs", ylab = "log of suboptimality", type = "l", main = "suboptimality of rcv1",lwd = 2)
lines(1:21, loss.imp.e, col = "orangered", lwd = 2)
lines(1:21, loss.uni.e, col = "dodgerblue", lwd = 2)
legend("topright", col = c("dodgerblue","orangered","gold"),lty = 1,lwd = 2, legend = c("uniform","importance", "gap-per-epoch"))
dev.off()
```
```{r plot rcv1 each iter}
gap.adagap.e <- process_result(read.csv("result/adagap_rcv_gap.csv"))[-1]
gap.imp.e <- process_result(read.csv("result/imp_rcv_gap.csv"))[-1]
gap.ssuni.e <- process_result(read.csv("result/ssuni_rcv_gap.csv"))[-1]
gap.adative.e <- process_result(read.csv("result/adative_rcv_gap.csv"))[-1]
gap.adauni.e <- process_result(read.csv("result/adauni_rcv_gap.csv"))[-1]

loss.adagap.e <- process_result(read.csv("result/adagap_rcv_loss.csv"))[-1]
loss.imp.e <- process_result(read.csv("result/imp_rcv_loss.csv"))[-1]
loss.ssuni.e <- process_result(read.csv("result/ssuni_rcv_loss.csv"))[-1]
loss.adative.e <- process_result(read.csv("result/adative_rcv_loss.csv"))[-1]
loss.adauni.e <- process_result(read.csv("result/adauni_rcv_loss.csv"))[-1]

gap.adagap.e <- c(gap0,gap.adagap.e[1:20])
gap.imp.e <- c(gap0,gap.imp.e[1:20])
gap.ssuni.e <- c(gap0,gap.ssuni.e[1:20])
gap.adative.e <- c(gap0,gap.adative.e[1:20])
gap.adauni.e <- c(gap0,gap.adauni.e[1:20])

loss.adagap.e <- c(loss0,2*loss.adagap.e[1:20])
loss.imp.e <- c(loss0,2*loss.imp.e[1:20])
loss.ssuni.e <- c(loss0,2*loss.ssuni.e[1:20])
loss.adative.e <- c(loss0,2*loss.adative.e[1:20])
loss.adauni.e <- c(loss0,2*loss.adauni.e[1:20])

jpeg("figure/rcv1_2.jpeg",width = 1200)
par(mfrow = c(1,2))
plot(1:21, gap.ssuni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of dual gap", type = "l",main = "dual gap of rcv1",lwd = 2, ylim = c(17,21))
lines(1:21, gap.adative.e, col = "orangered", lwd = 2)
lines(1:21, gap.adauni.e, col = "gold", lwd = 2)
lines(1:21, gap.adagap.e, col = "purple", lwd = 2)
lines(1:21, gap.imp.e, col = "lightcyan3", lty = 2, lwd = 2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","importance"))
plot(1:21, loss.ssuni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of suboptimality", type = "l",lwd=2, main = "suboptimality of rcv1")
lines(1:21, loss.adative.e, col = "orangered",lwd=2)
lines(1:21, loss.adauni.e, col = "gold",lwd=2)
lines(1:21, loss.adagap.e, col = "purple",lwd=2)
lines(1:21, loss.imp.e, col = "lightcyan3", lty = 2,lwd=2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","importance"))
dev.off()
```
```{r intial gap and loss of ionosphere}
gap0 <- 0
w <- A.ionosphere%*%rep(1,351)/0.1/((351)^2)
for (i in 1:351){
  gap0 <- gap0 + svm.gap(rep(1,351),0.1,A.ionosphere,i,y.ionosphere,w)
}
gap0 <- log(gap0)
loss0 <- svm.loss(A.ionosphere, rep(1,351), 0.1, y.ionosphere )
```

```{r plot ionosphere per epoch}
gap.adagap.e <- process_result(read.csv("svm/epoch_adagap_gap.csv"))[-1]
gap.uni.e <- process_result(read.csv("svm/epoch_uni_gap.csv"))[-1]
gap.imp.e <- process_result(read.csv("svm/epoch_imp_gap.csv"))[-1]
loss.adagap.e <- process_result(read.csv("svm/epoch_adagap_loss.csv"))[-1]
loss.uni.e <- process_result(read.csv("svm/epoch_uni_loss.csv"))[-1]
loss.imp.e <- process_result(read.csv("svm/epoch_imp_loss.csv"))[-1]
gap.adagap.e <- c(gap0,gap.adagap.e[1:9])
gap.uni.e <- c(gap0,gap.uni.e[1:9])
gap.imp.e <- c(gap0,gap.imp.e[1:9])
loss.adagap.e <- c(loss0,loss.adagap.e[1:9])
loss.uni.e <- c(loss0,loss.uni.e[1:9])
loss.imp.e <- c(loss0,loss.imp.e[1:9])
jpeg("figure/ionosphere1.jpeg",width = 1200)
par(mfrow = c(1,2))
plot(1:10, gap.adagap.e, col = "gold", xlab = "Epochs", ylab = "log of dual gap", type = "l",main = "dual gap of ionosphere", lwd = 2)
lines(1:10, gap.imp.e, col = "orangered", xlab = "Epochs", ylab = "log of dual gap", lwd =2 )
lines(1:10, gap.uni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of dual gap", type = "l", lwd =2)
legend("topright", col = c("dodgerblue","orangered","gold"),lwd=2,lty = 1, legend = c("uniform","importance", "gap-per-epoch"))
plot(1:10, loss.adagap.e, col = "gold", xlab = "Epochs", ylab = "value of objective function", type = "l", main = "objective function value of ionosphere",lwd = 2)
lines(1:10, loss.imp.e, col = "orangered", lwd = 2)
lines(1:10, loss.uni.e, col = "dodgerblue", lwd =2)
legend("topright", col = c("dodgerblue","orangered","gold"),lwd=2,lty = 1, legend = c("uniform","importance", "gap-per-epoch"))
dev.off()
```

```{r plot ionosphere each iter}
gap.adagap.e <- process_result(read.csv("svm/adagap_gap.csv"))[-1]
gap.uni.e <- process_result(read.csv("svm/uni_gap.csv"))[-1]
gap.ssuni.e <- process_result(read.csv("svm/ssuni_gap.csv"))[-1]
gap.adative.e <- process_result(read.csv("svm/adative_gap.csv"))[-1]
gap.adauni.e <- process_result(read.csv("svm/adauni_gap.csv"))[-1]

loss.adagap.e <- process_result(read.csv("svm/adagap_loss.csv"))[-1]
loss.uni.e <- process_result(read.csv("svm/uni_loss.csv"))[-1]
loss.ssuni.e <- process_result(read.csv("svm/ssuni_loss.csv"))[-1]
loss.adative.e <- process_result(read.csv("svm/adative_loss.csv"))[-1]
loss.adauni.e <- process_result(read.csv("svm/adauni_loss.csv"))[-1]

gap.adagap.e <- c(gap0,gap.adagap.e[1:9])
gap.uni.e <- c(gap0,gap.uni.e[1:9])
gap.ssuni.e <- c(gap0,gap.ssuni.e[1:9])
gap.adative.e <- c(gap0,gap.adative.e[1:9])
gap.adauni.e <- c(gap0,gap.adauni.e[1:9])

loss.adagap.e <- c(loss0,loss.adagap.e[1:9])
loss.uni.e <- c(loss0,loss.uni.e[1:9])
loss.ssuni.e <- c(loss0,loss.ssuni.e[1:9])
loss.adative.e <- c(loss0,loss.adative.e[1:9])
loss.adauni.e <- c(loss0,loss.adauni.e[1:9])

jpeg("figure/ionosphere2.jpeg",width = 1200)
par(mfrow = c(1,2))
plot(1:10, gap.ssuni.e, col = "dodgerblue", xlab = "Epochs", ylab = "log of dual gap", type = "l",main = "dual gap of ionosphere",lwd = 2)
lines(1:10, gap.adative.e, col = "orangered", lwd = 2)
lines(1:10, gap.adauni.e, col = "gold", lwd = 2)
lines(1:10, gap.adagap.e, col = "purple", lwd = 2)
lines(1:10, gap.uni.e, col = "lightcyan3", lty = 2, lwd = 2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","uniform"))
plot(1:10, loss.ssuni.e, col = "dodgerblue", xlab = "Epochs", ylab = "value of objective function", type = "l",lwd=2, main = "objective function value of ionosphere")
lines(1:10, loss.adative.e, col = "orangered",lwd=2)
lines(1:10, loss.adauni.e, col = "gold",lwd=2)
lines(1:10, loss.adagap.e, col = "purple",lwd=2)
lines(1:10, loss.uni.e, col = "lightcyan3", lty = 2,lwd=2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","uniform"))
dev.off()
```
```{r another plot of ionosphere}
jpeg("figure/ionosphere3.jpeg",width = 600)
plot(3:10, loss.ssuni.e[3:10], col = "dodgerblue", xlab = "Epochs", ylab = "value of objective function", type = "l",lwd=2, main = "objective function value of ionosphere")
lines(3:10, loss.adative.e[3:10], col = "orangered",lwd=2)
lines(3:10, loss.adauni.e[3:10], col = "gold",lwd=2)
lines(3:10, loss.adagap.e[3:10], col = "purple",lwd=2)
lines(3:10, loss.uni.e[3:10], col = "lightcyan3", lty = 2,lwd=2)
legend("topright", col = c("dodgerblue","orangered","gold","purple","lightcyan3"),lty = c(1,1,1,1,2),lwd = 2, legend = c("supportSet-uniform","adative","ada-uniform","ada-gap","uniform"))
dev.off()
```